---
title: "MNcalc-NEWS"
author: "Erik.Leppo@tetratech.com"
date: "`r Sys.time()`"
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# MNcalc 0.2.0.9020 (2024-07-23)

* docs: Update NEWS
* refactor: Update version number

# MNcalc 0.2.0.9019 (2024-07-23)

* refactor: Add "_ORIG" metrics for IBI calculations in server.R
    + bugs and fish for all classes
    + Add to files
       - IBI_2metval_all.csv
       - IBI_2metval_IBI.csv
       - _IBI_RESULTS.csv
       
# MNcalc 0.2.0.9018 (2024-07-23)      

* refactor: Updates to About and References UI tabs       

# MNcalc 0.2.0.9017 (2024-07-18)


# MNcalc 0.2.0.9016 (2024-07-18)

* refactor: Clean up
    + Remove unused code from Server.R
    + Remove unused tabs
    + Remove unused RMD files
* fix: Update ouput for BCG calculation in Server.R
    + BCG_2metvall_all.csv to BCG_2metval_all.csv
* refactor: Update calculation and file builder code for any issues
* docs: Add pull request updates to NEWS

# MNcalc 0.2.0.9015 (2024-07-16)

* refactor: Minor update to styling of a table in the UI

# MNcalc 0.2.0.9014 (2024-07-15)

* refactor: Reformatted UI for the file builder section
    + New language, tables, and figures provided by Jen

# MNcalc 0.2.0.9013 (2024-07-15)

* refactor: 
Updated UI for calculation tabs with new language, tables, and figures

# MNcalc 0.2.0.9012 (2024-07-12)

* refactor: Updated about tab, reference tab, and added troubleshooting tab

# MNcalc 0.2.0.9011 (2024-07-05)

* refactor: Update naming scheme for result files
    + BCG
    + IBI
    + taxa translate
* refactor: taxa translate file names prefix with BCG/IBI but not Bugs/Fish
    + Already in subfolder with assemblage name

# MNcalc 0.2.0.9010 (2024-07-05)

* refactor: Update TaxaTranslator result folders to match calculations folders
    + TaxaTrans was lower case and calc was first letter cap for assemblage

# MNcalc 0.2.0.9009 (2024-07-05)

* refactor: Update URL references in Server.R for support files
* refactor: Update TaxaTranslator result folder (typo for bugs ibi)

# MNcalc 0.2.0.9008 (2024-07-05)

* refactor: Update Global.R for new location of support files

# MNcalc 0.2.0.9007 (2024-07-03)

* refactor: Update links in Reference to GitHub raw
    + Will download instead of open

# MNcalc 0.2.0.9006 (2024-07-03)

* refactor: Update links in References to pull from GitHub so open in new tab
* refactor: Change names of Reference PDFs
* refactor: Update zip file with all reference PDFs

# MNcalc 0.2.0.9005 (2024-07-02)

* refactor: Update About page

# MNcalc 0.2.0.9004 (2024-06-13)

* refactor: Update file builder taxa translator
    + Add Index_Name as a required field
    + Update pop ups for Index_Name, Index_Class, and GP/RR
    + Ensure Index_Name, Index_Class, and GP/RR are carried through to results,
    Issue #8

# MNcalc 0.2.0.9003 (2024-06-13)

* refactor: Remove text about additional fields on file builder, Issue #9

# MNcalc 0.2.0.9002 (2024-06-13)

* refactor: Update file builder pop up to include number of mismatches, Issue #13

# MNcalc 0.2.0.9001 (2024-06-13)

* fix: Update complete pop up for misspelling, Issue #12

# MNcalc 0.2.0 (2024-06-12)

* refactor: Update version number for deliverable

# MNcalc 0.1.0.9019 (2024-06-12)

* refactor: Add conditions for no matches for taxa translator

# MNcalc 0.1.0.9018 (2024-06-12)

* refactor: Add pop up to ensure BCG community selection matches data, Issue#6
* refactor: Uncomment the BIBI metric input transformations

# MNcalc 0.1.0.9017 (2024-06-12)

* feature: Add .simpleCaps function from `toupper` help
    + Shiny app, scripts; helper_functions.R
* refactor: Add pop up to ensure IBI community selection matches data
* refactor: Rename RedLake to MN, Issue #4
    + About
    + Apps directory
    + UI.R app title
    + NEWS
    + DESCRIPTION
    + README
* refactor: Ensure use RedLake not RedLakes

# MNcalc 0.1.0.9016 (2024-06-10)

* refactor: Update Fish IBI post calculation adjustments

# MNcalc 0.1.0.9015 (2024-06-06)

* refactor: Update Fish IBI post Index calculation adjustments
    + Low End Scoring
    + percent DELT adjustment

# MNcalc 0.1.0.9014 (2024-06-04)

* fix: Update file to avoid readxl import message
    + data/BCGcalc_Shiny_map_inputs_20230828.xlsx

# MNcalc 0.1.0.9013 (2024-06-04)

* fix: Change IBI Calc output tab from "Calc_BCG_Ouput" to "Calc_IBI_Output"
* refactor: New PC so more files showing as changed

# MNcalc 0.1.0.9012 (2024-01-10)

* feature: Add IBI calculation to Shiny app

# MNcalc 0.1.0.9011 (2023-12-21)

* refactor: Calculation community buttons to default to NA
    + calc_BCG
    + calc_thermalfuzzy
    + calc_thermalmetrics

# MNcalc 0.1.0.9110 (2023-12-14)

* refactor: Modify results subfolder to include community
    + Taxa Translate
    + Calculate BCG  (and later IBI)

# MNcalc 0.1.0.9009 (2023-12-14)

* refactor: Auto add INDEX_NAME if missing for BCG calculation

# MNcalc 0.1.0.9008 (2023-12-14)

* refactor: Update on-screen text from OR-WA to MN
* refactor: Add MN BCG and IBI documentation
* refactor: Remove some OR-WA specific files

# MNcalc 0.1.0.9007 (2023-12-13)

* refactor: Update language on screen for calculations
    + BCG to BCG and IBI
* fix: Update output for calculations results when no flags
* refactor: Add files to results reference file
    + MetricNames.xlsx
    + MetricScoring.xlsx
    + Rules.xlsx
    + MetricFlags.xlsx
    + IndexClass.xlsx
* refactor: Update code for downloading reference files from GitHub
    + global.R
    + server.R
* fix: Update taxa translate mutate case_when
    + fails if columns not the same class

# MNcalc 0.1.0.9006 (2023-12-07)

* refactor: modify global packages order

# MNcalc 0.1.0.9005 (2023-12-07)

* refactor: Add complete pop up to merge files

# MNcalc 0.1.0.9004 (2023-12-07)

* fix: Update app BCG calculation for cases where have no flags
    + Same as BCGcalc v2.0.0.9126 commit

# MNcalc 0.1.0.9003 (2023-12-05)

* refactor: Update Shiny to work with Red Lakes data
  + Rename App
  + Update import routine for multiple BCG_ATTR columns
  + Update taxa translate for Red Lakes (more user fields)
  + Comment out sections of app not using for Red Lakes
  + Update ReadMe in app
  + Add routine for generating ecoregion
  + Add information to BCG calculation when not the correct region
      - Include output file
  + Remove MTTI model (OR-WA specific)

# MNcalc 0.1.0.9002 (2023-12-05)

* feature: Add Shiny app files from BCGcalc, v2.0.0.9112 (2023-12-04)

# MNcalc 0.1.0.9001 (2023-12-05)

* docs: Add base package files
   + DESCRIPTION
   + NEWS
   + README
   + app function

# MNcalc 0.1.0 (2023-12-05)

* Created GitHub repository

