---
title: "RedLakesCalc-README"
author: "Erik.Leppo@tetratech.com"
date: "`r Sys.time()`"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE
                      , collapse = TRUE
                      , comment = "#>"
                      , fig.path = "README-")

```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```
# RedLakesCalc
Biological Condition Gradient (BCG) and Index of Biotic Integrity (IBI)
calculator Shiny app.  For the Red Lakes Tribe in Minnesota.  Calculates the MN
state BCG and IBI in a Shiny app using the BioMonTools and BCGcalc R packages.

Badges
-----------
to come later

Installation
-----------------
To install the current version use the code below to install from GitHub. The 
use of “force = TRUE” ensures the package is installed even if already present. 
If the package `remotes` is missing the code below will install it.

```{r Install, eval=FALSE}
if(!require(remotes)){install.packages("remotes")}  #install if needed
install_github("leppott/RedLakesCalc", force=TRUE)
```

Purpose
--------------
To aid users in the calculation of the MN BCG and IBI (bugs and fish).

Usage
------------
After installing the package can launch the app using the code below.
```{r usage, eval=FALSE}
app("RedLakesCalc")
```

Shiny
------------
The Shiny app code is included in the package but is also on the web.

https://tetratech-wtr-wne.shinyapps.io/RedLakesCalc/
